A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-28 paper.tex
Work in progress
General tables and images upgrade.

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig1_background.pdf}
    \caption{These ideas planted the seed of thought in our current presentation.} \label{fig1}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig2_proposal.pdf}
    \caption{Algorithm model inspired by the animal species' biological Life-Cycle.} \label{fig2}
    \end{figure}

@@

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig3_newtonslaw.pdf}
    \caption{Newton's Law of Universal Gravitation.} \label{fig3}
    \end{figure}

Where:
•	F is the gravitational force acting between two objects
•	m1 and m2 are the masses of the objects
•	r is the distance between the centers of their masses
•	G is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2

@@

For each experiment, we ran 60 independent executions per algorithm and
recorded the following results: Last Generation, Total Evaluations, Time
(seconds), Evaluations/second.

•	Last Gen.: The generation that found the solution.
•	Eval.: The total number of evaluations the algorithm executed. 
•	Time (sec): Total elapsed or wall clock time, in seconds. 
•	Eval/sec: The calculated rate of evaluations per second.

@@

The following tables will be removed from the document.

    Table~\ref{tab3} shows the OneMax DEAP experiment results, while Table~\ref{tab4} shows the LifeCycle Algorithm experiment results.

    \begin{table}[]
        \centering        
        \caption{OneMax DEAP experiment results.}\label{tab6}        
        \begin{tabular}{|l|l|l|l|l|}
        \hline
        \multicolumn{5}{|c|}{\textbf{OneMax DEAP}} \\ \hline
        \begin{tabular}[c]{@{}l@{}}Run   \\    \\ No.\end{tabular} & Generation & \begin{tabular}[c]{@{}l@{}}Best \\    \\ Individual\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total\\    \\ Evaluations\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total Time \\    \\ (seconds)\end{tabular} \\ \hline
        1 & 6 & 20 & 360 & 0.016 \\ \hline
        2 & 5 & 20 & 300 & 0.032 \\ \hline
        3 & 7 & 20 & 420 & 0.061 \\ \hline
        4 & 9 & 20 & 540 & 0.081 \\ \hline
        5 & 8 & 20 & 480 & 0.080 \\ \hline
        6 & 6 & 20 & 360 & 0.062 \\ \hline
        7 & 7 & 20 & 420 & 0.062 \\ \hline
        8 & 6 & 20 & 360 & 0.016 \\ \hline
        9 & 8 & 20 & 480 & 0.058 \\ \hline
        10 & 6 & 20 & 360 & 0.050 \\ \hline
        11 & 7 & 20 & 420 & 0.073 \\ \hline
        12 & 8 & 20 & 480 & 0.076 \\ \hline
        13 & 8 & 20 & 480 & 0.065 \\ \hline
        14 & 6 & 20 & 360 & 0.060 \\ \hline
        15 & 6 & 20 & 360 & 0.045 \\ \hline
        16 & 6 & 20 & 360 & 0.059 \\ \hline
        17 & 6 & 20 & 360 & 0.061 \\ \hline
        18 & 6 & 20 & 360 & 0.058 \\ \hline
        19 & 5 & 20 & 300 & 0.060 \\ \hline
        20 & 7 & 20 & 420 & 0.067 \\ \hline
        21 & 7 & 20 & 420 & 0.060 \\ \hline
        22 & 7 & 20 & 420 & 0.085 \\ \hline
        23 & 7 & 20 & 420 & 0.071 \\ \hline
        24 & 4 & 20 & 300 & 0.049 \\ \hline
        25 & 6 & 20 & 360 & 0.050 \\ \hline
        26 & 9 & 20 & 540 & 0.081 \\ \hline
        27 & 6 & 20 & 420 & 0.074 \\ \hline
        28 & 6 & 20 & 360 & 0.064 \\ \hline
        29 & 6 & 20 & 360 & 0.065 \\ \hline
        30 & 4 & 20 & 240 & 0.016 \\ \hline
        Avg. & 6.5 & 20 & 394 & 0.059 \\ \hline
        \end{tabular}
        \end{table}

    \begin{table}[]
        \centering        
        \caption{LifeCycle Algorithm experiment results.}\label{tab7}
        \begin{tabular}{|l|l|l|l|l|}
        \hline
        \multicolumn{5}{|c|}{\textbf{LifeCycle Algorithm}} \\ \hline
        \begin{tabular}[c]{@{}l@{}}Run   \\    \\ No.\end{tabular} & Generation & \begin{tabular}[c]{@{}l@{}}Best \\    \\ Individual\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total\\    \\ Evaluations\end{tabular} & \begin{tabular}[c]{@{}l@{}}Total Time \\    \\ (seconds)\end{tabular} \\ \hline
        1 & 8 & 20 & 486 & 6.65 \\ \hline
        2 & 6 & 20 & 381 & 5.20 \\ \hline
        3 & 6 & 20 & 369 & 5.69 \\ \hline
        4 & 7 & 20 & 434 & 6.37 \\ \hline
        5 & 12 & 20 & 731 & 8.20 \\ \hline
        6 & 5 & 20 & 306 & 4.55 \\ \hline
        7 & 13 & 20 & 764 & 8.34 \\ \hline
        8 & 4 & 20 & 233 & 4.09 \\ \hline
        9 & 12 & 20 & 692 & 7.27 \\ \hline
        10 & 6 & 20 & 338 & 4.76 \\ \hline
        11 & 9 & 20 & 559 & 7.78 \\ \hline
        12 & 12 & 20 & 730 & 8.35 \\ \hline
        13 & 4 & 20 & 219 & 3.43 \\ \hline
        14 & 8 & 20 & 462 & 5.28 \\ \hline
        15 & 4 & 20 & 217 & 3.37 \\ \hline
        16 & 4 & 20 & 234 & 4.54 \\ \hline
        17 & 4 & 20 & 256 & 4.35 \\ \hline
        18 & 12 & 20 & 714 & 8.14 \\ \hline
        19 & 12 & 20 & 694 & 7.88 \\ \hline
        20 & 15 & 20 & 892 & 9.74 \\ \hline
        21 & 11 & 20 & 633 & 7.98 \\ \hline
        22 & 3 & 20 & 169 & 4.02 \\ \hline
        23 & 10 & 20 & 611 & 6.89 \\ \hline
        24 & 10 & 20 & 629 & 7.32 \\ \hline
        25 & 7 & 20 & 416 & 6.22 \\ \hline
        26 & 7 & 20 & 446 & 5.55 \\ \hline
        27 & 6 & 20 & 379 & 5.95 \\ \hline
        28 & 8 & 20 & 466 & 6.98 \\ \hline
        29 & 3 & 20 & 197 & 3.36 \\ \hline
        30 & 6 & 20 & 381 & 6.16 \\ \hline
        Avg. & 7.8 & 20 & 468 & 6.15 \\ \hline
        \end{tabular}
        \end{table}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=80mm]{img/fig1_background.pdf}
    \caption{These ideas planted the seed of thought in our current presentation.} \label{fig1}
    \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=70mm]{img/fig2_proposal.pdf}
    \caption{Algorithm model inspired by the animal species' biological Life-Cycle.} \label{fig2}
    \end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=50mm]{img/fig3_newtonslaw.pdf}
    \caption{Newton's Law of Universal Gravitation.} \label{fig3}
    \end{figure}

Where:
\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
    \item[$\bullet$ F] is the gravitational force acting between two objects
    \item[$\bullet$ m1 and m2] are the masses of the objects
    \item[$\bullet$ r]	is the distance between the centers of their masses
    \item[$\bullet$ G]	is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2
\end{description}

@@

For each experiment, we ran 60 independent executions per algorithm and
recorded the following results: Last Generation, Total Evaluations, Time
(seconds), Evaluations/second. The labels used on the table header are the
following:

\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
    \item[$\bullet$ Last Gen.:] The generation that found the solution.
    \item[$\bullet$ Eval.:] The total number of evaluations the algorithm executed. 
    \item[$\bullet$ Time (sec):] Total elapsed or wall clock time, in seconds. 
    \item[$\bullet$ Eval/sec:] The calculated rate of evaluations per second.
\end{description}

@@

% Table~\ref{tab3} shows the OneMax DEAP experiment results, while Table~\ref{tab4} shows the LifeCycle Algorithm experiment results.
